Sustainable Pathways for Irish homes in changing TIMES

### 2021-07-16 manuscript.tex
Finishing Results!

Demand TIMESLICE

Energy service demands in the residential sector are driven by the total dwelling stock for non-archetype energy services or apartment, attached or detached dwelling stock for archetype energy services, which in turn is driven by population growth and the occupancy rate (the average number of people per dwelling). The residential stock projections up to 2040 are taken from Economic and Social Research Institute's (ESRI's) housing demand estimates \cite{BerginREGIONALLEVEL}.
Archetype energy service demands are dependant on both the type of dwelling and whether it is existing or new. The average archetype energy service in new and existing is shown in Table \ref{Archetype Energy Service Demands}
\begin{table}[htbp]
  \centering
  \footnotesize
  \caption{Archetype Energy Service Demands}
 \begin{tabular}{c|cc|cc|cc}
 \hline
 \multicolumn{1}{c|}{Energy Service}  & \multicolumn{2}{c|}{Apartments} & \multicolumn{2}{c|}{Attached} & \multicolumn{2}{c}{Detached}  \\
  \multicolumn{1}{c|}{}  & \multicolumn{2}{c|}{($kWh/house/yr$)} & \multicolumn{2}{c|}{($kWh/house/yr$)} & \multicolumn{2}{c}{($kWh/house/yr$)}  \\
  & Existing & New & Existing & New & Existing & New \\
 \hline
 Space Heating & 3,853 & 1,228 & 7,852 & 2,845 & 14,405 & 6,745 \\
 Water Heating & 3,409 & 2,197 & 3,011 & 2,351 & 3,806 & 2,493 \\
 Lighting & 179 & 156 & 254 & 229 & 419 & 392  \\
 Pumps \& Fans  & 55  & 60 & 106 & 104 & 131 & 110  \\
 Space Cooling  & 0 & 60 & 0 & 104 & 0 & 110  \\
 \hline
 \end{tabular}
 \label{Archetype Energy Service Demands}
\end{table}

@@

Also non- archetype energy servies demands -

%% Ask Ankita for more info about Demand Calculations!!
%Compound Annual Growth Rate (CAGR)
%The occupancy rate is expected to fall to 2.12 in 2051 \citep{PropertyIndustryIreland2019}, from 2.75 in 2016 (CSO).

%  Intermediate values are estimated using Equation \ref{eq:OR}.
% \begin{equation}
% \label{eq:OR}
%  OR= a+b*log(\Delta t)
% \end{equation}
% here, $OR$ is the occupancy rate, $\Delta t$ is difference between years, parameters $a$ \& $b$ are estimated using historical values.

@@

% Energy service demands in the residential sector are driven by the size of the housing stock by type (apartment, attached or detached), which in turn is driven by population growth and the occupancy rate, the average number of people per dwelling. The occupancy rate is expected to fall to 2.12 in 2051 \citep{PropertyIndustryIreland2019}, from 2.75 in 2016 (CSO). Intermediate values are estimated using Equation \ref{eq:OR}.
% \begin{equation}
% \label{eq:OR}
%  OR= a+b*log(\Delta t)
% \end{equation}
% here, $OR$ is the occupancy rate, $\Delta t$ is difference between years, parameters $a$ \& $b$ are estimated using historical values. 
\begin{table}[htbp]
\footnotesize
 \centering
 \caption{Energy service demands in TIM}

% \begin{tabular}{p{18em}lccc}
% \hline
%    \multirow{Energy Service Demand} & \multirow{Driver} & %\multicolumn{2}{c}{Value} & \multirow{Unit} \\
%          &       & \multicolumn{1}{c}{2018} & \multicolumn{1}{c}{2050} &  \\ \hline
%    Residential Apartment Demand & Population & 206.80 & 628.93 & 000' \\
 %   Residential Attached Demand & Population & 766.35 & 1056.50 & 000' \\
 %   Residential Detached Demand & Population & 724.43 & 889.76 & 000' \\
%    \hline
%    \end{tabular}%

  \label{tab:ESD_list}%
\end{table}%

% Table generated by Excel2LaTeX from sheet 'Population'
\begin{table}[htbp]
 \centering
 \footnotesize
 \caption{Population}
 \begin{tabular}{cc}
 \hline
 Year & Population (millions) \\
 \hline
 2018 & 4.85 \\
 2020 & 4.98 \\
 2030 & 5.40 \\
 2040 & 5.82 \\
 2050 & 6.19 \\
 \hline
 \end{tabular}%
 \label{tab:pop}%
\end{table}%

@@

%\begin{figure}[!htbp]
%\centering
%\begin{tikzpicture}
%\begin{axis}[
%    x tick label style={
%		/pgf/number format/1000 sep=}, xlabel={Year},
%	y tick label style={
%	    /pgf/number},
%		ylabel={Energy Consumption($ktoe$)},
%		 scaled y ticks = false,
%    xmin=2000, xmax=2050,
%    ymin=0, ymax=40,
%    xtick={2000,2010,2020,2030,2040,2050},
 %   ytick={0,10,20,30,40},
 %   ymajorgrids=true,
%]
%\addplot[
%    color=blue,
%    mark=square,
%    ]
%    coordinates {
%    (2000,0.6)(2010,3.1)(2020,8.4)(2030,16.3)(2040,26.1)(2050,37)
 %   };
%    
%\end{axis}
%\end{tikzpicture}
%    \caption{Space Cooling Residential Energy Consumption (Source: POTEnCIA) }
 %   \label{fig:Cooling}
%\end{figure}

@@

\subsubsection{User Constraints}
\label{LitR:Constraints}
The TIM model operates on the basis of perfect foresight, but
\textit{``in reality, the behaviours of consumers is not always economically rational"} \cite{Li2018IncorporatingModel} for this reason ``User Constraints" are applied in the residential sector to better reflect reality. The User Constraints applied to the residential sector include:
\begin{itemize}
 \item One Space and Water Heating System per household ( stoves excluded ) 
 \item Maximum 60\% of existing buildings to be retrofitted by 2030, and 95 \% by 2070. Maximum \% interpolated between 2030 and 2070. 
 \item The natural gas grid is currently connected to 39\% of apartments, 52\% of attached dwellings and 12\% of detached dwellings. The total share of dwellings connected to the gas grid is an upper constraint to grow by 50\% for each archetype. 
\item Maximum fuel share in cooking for Gas and LPG is 40\% and 10\% respectively. Base year fuel share for Gas is 32\% and LPG is 1.5 \%.
\item Maximum 10\% solar input to dual fuel heating technology
\item Maximum 30\% gas input into gas hybrid heating pumps
\end{itemize}

@@

\section{Results}
\label{Results}
Electricity Supply, Technology and Fuel Mix, Retrofitting, Cost

The final version of the newly developed TIM provides some valuable insights on each sector and the sectoral interconnections. The results outlined in this paper are based upon six scenarios. TIM can only analysis the energy system, the other large source of GHG emissions is from agriculture, therefore some scenarios are labelled based on agriculture GHG reduction (AXX) and Energy System GHG reduction (EXX), the six scenarios are:
\begin{itemize}
    \item \textbf{No Mitigation} Least cost solution, where no emissions constraints are imposed
    \item \textbf{With Additional Measures (WAM)} includes the implementation of Ireland’s CAP 2019.
    \item \textbf{A25E65} Agriculture GHG emissions reduce by 25\%, Energy system GHG emissions reduces by 65\% by 2030 compared to 2018.
    \item \textbf{A33E61} Agriculture GHGs reduces by 33\% and Energy system GHGs by 61\%
    \item \textbf{A40E57} Agriculture GHGs reduces by 33\% and Energy system GHGs by 61\%
    \item \textbf{A51E51} Equal GHG reduction share in of 51 \% in Agriculture and Energy Systems. 
\end{itemize}

While the first two scenarios do not comply with the overall 51 \% GHG reduction in 2030 compared to 2018 or net-zero by 2050, however they do provide insights on the incremental steps required. The last four scenarios comply with the overall 51 \% target and net-zero by 2050 and offer insights about different trajectories to achieve those targets.  
Under CAP 2019 agriculture, GHG emission reduction is 10-15\% on the projected levels in 2030 relative to 2017. The higher agriculture ambition explored GHG reductions of 25-51\%.

XXX % PICK UP HERE

@@

\section{Discussion}
\label{Discussion}
5\% increase of residential energy in 2030 when internal temperatures are adjusted. 
Soft-linking with LEAP and PLEXOS
%o	Discuss and interpret the results
%o	Focus on what added value the model brings
%o	Also include future development priorities here
%o	What can’t the model do? Where is it more suitable to use another model - Hannah Email
Retrofitting ``rebound" saving orangeuces energy other is more difficult to measure like improved physical and mental health. 
\subsection{Strengths}
\label{Dis:Strengths}

@@

\subsection{Limitations}
\label{Dis:Limit}
BER Database - No PV Solar capacity, No Heat Pump ready, Large defaults, wall types check?)
%Discrepancies were investigated, and assumptions reviewed intuitively in order to achieve a good match.=
Consumers’ final investment decision can be
represented by “willingness-to-pay” curves – for
instance, around 10\% of owner-occupiers are willing
to invest in energy efficiency measures for a payback
time of 4 years, falling to 0\% for a payback time of
6 years for some consumer cohorts
Type of Tenure is ignoorange
BER aggeragateed
housing stock u-values
behaviour and occupancy
Area
expected energy consumption weakness of BER database as 
Actual energy consumption for dwellings of
similar or near identical construction may vary by up to 600%
depending on usage \cite{Sunikka-Blank2012BuildingConsumption}
\section{Conclusions}
\label{Conclusion}
This paper reports results on an ambitious mitigation target in the period to 2050 for the Irish energy system. The analysis has been performed using the Irish TIMES model
\textit{We stress the importance of differentiating between technical con-
straints and behavioural constraints in optimisation models. Including both conflates what is consideorange desirable under the economic welfare paradigm (i.e. cost-minimising decisions) with “realistic decisions”, complicating the interpretation of the results. Optimisation models are by design well suited to study cost-optimal behaviour, and running scenarios just with technical constraints facilitates the identification of areas where market barriers are more entrenched, and interventions to accelerate the uptake of low-carbon practices may be needed.} \cite{Astudillo2017CanModelb}
\section{Acknowledgements}
\label{sec:Acknowledgements}
Tomas %CAPACITY is funded under the Climate Action Modelling Group (CAMG) by DECC
% https://www.marei.ie/project/capacity/
CHIMERA is supported by a research grant from Science Foundation Ireland (SFI) and the National Natural Science Foundation of China (NSFC) under the SFI-NSFC Partnership Programme, grant no. 17/NSFC/5181 and
supported by MaREI, the SFI Research Centre for Energy, Climate, and Marine [Grant No: 12/RC/2302\_P2]

>>>>

Energy service demands in the residential sector are driven by the total dwelling stock for non-archetype energy services and apartment, attached or detached dwelling stock for archetype energy services, which in turn is driven by population growth and the occupancy rate (the average number of people per dwelling). The residential stock projections up to 2040 are taken from Economic and Social Research Institute's (ESRI's) housing demand estimates \cite{BerginREGIONALLEVEL}. However, there is archetpye specfic growth is limited or unavailable, for this reason a simple linear regression is used to calculate archertype growth. Table \ref{Table:DwellingGrowth} shows the growth rate for historical years (2016-2020) and the future years (2020 onwards). The growth rate of apartments is the highest and increasing up to 2040, while attached and detached dwelling types is decreasing, indicating a preference for smaller dwellings and compact urban planning to rise in the future.

\begin{table}[htbp]
  \centering
  \footnotesize
  \caption{Dwelling Growth}
\begin{tabular}{l|lcc}
Years & Apartment & \multicolumn{1}{l}{Attached } & \multicolumn{1}{l}{Detached} \\ \hline
2016-2020  & 2.89\%   & 1.69\%     & 1.58\%     \\
\hline
2020-2030     & 4.26\%   & 1.15\%     & 0.81\%   \\
2030-2040     & 3.33\%   & 0.89\%     & 0.53\%   \\
2040-2050     & 2.47\%   & 0.52\%     & 0.14\%   \\
\end{tabular}
\label{Table:DwellingGrowth}
\end{table}
Archetype energy service demands are dependant on both the type of dwelling and whether it is existing or new. The average archetype energy service in new and existing is shown in Table \ref{Archetype Energy Service Demands}
\begin{table}[htbp]
  \centering
  \footnotesize
  \caption{Archetype Energy Service Demands}
 \begin{tabular}{c|cc|cc|cc}
 \hline
 \multicolumn{1}{c|}{Energy Service}  & \multicolumn{2}{c|}{Apartments} & \multicolumn{2}{c|}{Attached} & \multicolumn{2}{c}{Detached}  \\
  \multicolumn{1}{c|}{}  & \multicolumn{2}{c|}{($kWh/house/yr$)} & \multicolumn{2}{c|}{($kWh/house/yr$)} & \multicolumn{2}{c}{($kWh/house/yr$)}  \\
  & Existing & New & Existing & New & Existing & New \\
 \hline
 Space Heating & 3,853 & 1,228 & 7,852 & 2,845 & 14,405 & 6,745 \\
 Water Heating & 3,409 & 2,197 & 3,011 & 2,351 & 3,806 & 2,493 \\
 Lighting & 179 & 156 & 254 & 229 & 419 & 392  \\
 Pumps \& Fans  & 55  & 60 & 106 & 104 & 131 & 110  \\
 Space Cooling  & 0 & 60 & 0 & 104 & 0 & 110  \\
 \hline
 \end{tabular}
 \label{Archetype Energy Service Demands}
\end{table}

@@

@@

% Energy service demands in the residential sector are driven by the size of the housing stock by type (apartment, attached or detached), which in turn is driven by population growth and the occupancy rate, the average number of people per dwelling. The occupancy rate is expected to fall to 2.12 in 2051 \citep{PropertyIndustryIreland2019}, from 2.75 in 2016 (CSO). Intermediate values are estimated using Equation \ref{eq:OR}.
% \begin{equation}
% \label{eq:OR}
%  OR= a+b*log(\Delta t)
% \end{equation}
% here, $OR$ is the occupancy rate, $\Delta t$ is difference between years, parameters $a$ \& $b$ are estimated using historical values.

@@

Demand TIMESLICE 40

@@

\subsubsection{User Constraints}
\label{LitR:Constraints}
The TIM model operates on the basis of perfect foresight, but
\textit{``in reality, the behaviours of consumers is not always economically rational"} \cite{Li2018IncorporatingModel} for this reason ``User Constraints" are applied in the residential sector to better reflect reality. The User Constraints applied to the residential sector include:
\begin{itemize}
 \item One Space and Water Heating System per household ( stoves excluded ) 
 \item Maximum 60\% of existing buildings to be retrofitted by 2030, and 95 \% by 2070. Maximum \% interpolated between 2030 and 2070. 
 \item A prerequisite electrical heat pump requirement is applied to each archetype, the percentage of dwellings which requires a shallow or deep retrofit before a heat pump can be installed (  B2 rating for heat pump ready dwelling ). Hybrid heat pumps are not included in this constraint. 
 \begin{table}[htbp]
  \centering
  \footnotesize
  \caption{Prerequisite Heat Pump Requirement}
    \begin{tabular}{r|rrr}
    \hline
    \multicolumn{1}{l}{Requirement} & \multicolumn{1}{l}{Apartment} & \multicolumn{1}{l}{Attached } & \multicolumn{1}{l}{Detached} \\ \hline
    No Retrofit  & 24.5 \%   & 14.3 \%   & 12 \% \\
    Shallow Retrofit  & 28.5 \%   & 34.7 \%  & 36.8 \% \\
    Deep Retrofit  & 47 \%   & 51 \%  & 51.2 \% \\
    \end{tabular}%
  \label{tab:HeatPumpConstraint}%
\end{table}%
 \item The natural gas grid is currently connected to 39\% of apartments, 52\% of attached dwellings and 12\% of detached dwellings. The total share of dwellings connected to the gas grid is an upper constraint to grow by 50\% for each archetype. 
\item Maximum fuel share in cooking for Gas and LPG is 40\% and 10\% respectively. Base year fuel share for Gas is 32\% and LPG is 1.5 \%.
\item Maximum 10\% solar input to dual fuel heating technology
\item Maximum 30\% gas input into gas hybrid heating pumps
\end{itemize}

@@

\section{Results}
\label{Results}

The newly developed TIM provides some valuable insights on each sector and the sectoral interconnections. The results outlined in this paper are based upon six scenarios. While TIM can only analysis the energy system, the other large source of GHG emissions is from agriculture, therefore some scenarios are labelled based on agriculture GHG reduction percentage and Energy System GHG reduction percentage, the six scenarios are:
\begin{itemize}
    \item \textbf{No Mitigation} Least cost solution, where no emissions constraints are imposed
    \item \textbf{With Additional Measures (WAM)} includes the implementation of Ireland’s CAP 2019.
    \item \textbf{A25E65} Agriculture GHG emissions reduce by 25\%, Energy system GHG emissions reduces by 65\% by 2030 compared to 2018.
    \item \textbf{A33E61} Agriculture GHGs reduces by 33\% and Energy system GHGs by 61\%
    \item \textbf{A40E57} Agriculture GHGs reduces by 33\% and Energy system GHGs by 61\%
    \item \textbf{A51E51} Equal GHG reduction share in of 51 \% in Agriculture and Energy Systems. 
\end{itemize}

While the first two scenarios do not comply with the Climate Action and Low Carbon Development (Amendment) Act 2021 target of an overall 51 \% GHG reduction in 2030 compared to 2018 or net-zero by 2050, however they do provide insights on the incremental steps required. The last four scenarios comply with 2030 and 2050 targets and offer insights about different trajectories to achieve those targets.  
Under CAP 2019 agriculture, GHG emission reduction is 10-15\% on the projected levels in 2030 relative to 2017. The higher agriculture ambition explored GHG reductions of 25-51\%.

Figure \ref{fig:$CO_2$ Waterfall} provides an overview of  scenario affects on each sector in 2030, as the energy system ambition increases incrementally from left to right.

@@

The share of sectoral $CO_2$ emissions is not evenly spread in 2018 and the optimal share of sectoral $CO_2$ reductions in 2030 is also unevenly distributed. In the A51E51 scenario, the optimal electricity annual emissions reduction is $7.1 MtCO_2$ in 2030, while transport currently emits the similiar $CO_2$ levels only reduces by $4.5 MtCO_2$. The residential sector reduces $CO_2$ emission by 63\% in A51E51 in 2030, electricity is 60 \% and transport is 38\%. Not only does Figure \ref{fig:$CO_2$ Waterfall} show the different optimal sectoral reductions, but also the ``low hanging fruit" in the large electricity reduction to the    ``high coconuts" in the step from A33E61 to A25E65, transport mitigates the majority of $CO_2$ emissions required.

Zooming in and focusing on the fuel-mix within the residential sector gives further insights on the optimal pathways to achieve 2030 targets, Figure \ref{fig:ResFuel} shows this, with the base year stacked chart on the top row, the four climate bill compliant scenarios on rows 2-5 and the last two rows are non-compliant.

\begin{figure}[!htbp]
 \centering
 \includegraphics[width=\textwidth]{Figures/RSD_Fuel2.png}
 \caption{Residential Fuel per scenario}
 \label{fig:ResFuel}
\end{figure}

In 2018, the residential sector had 124 PJ of primary energy that figure needs to decrease by 8-13 \% in 2030, to comply with climate targets. While Figure \ref{fig:$CO_2$ Waterfall} shows the large $CO_2$ reduction in electricity, this translates to a Figure \ref{fig:ResFuel} representing a large uptake of electricity in the residential sector within climate bill compliant scenarios. The large increase in ambient energy indicates the type of technology deployed in the residential sector, more on this in Figure XXX. The overall share of ambient heat increases from 1.4 \% in 2019 to between 13-26 \% in 2030. as a fuel  In climate bill compliant sceanrios peat and coal are completely phased out, while oil use decreases 90-93 \% by 2030. Gas energy increase by 34 \% in the A51E51 scenario, but remains relatively stable amoung other climate bill compliant sceanrios in 2030. 
By comparing compliant and noncompliant sceanrios, we can observe the favoured fuels and technologies, while also observing the incremental steps of emission reduction and overall cost change with each sceanrio.

While Figure \ref{fig:ResFuel} shows the primary energy redcution required, it must be noted that retrofits are used to reduce the primary energy required ( reduced energy through behavioural change is not modelled ). Figure \ref{fig:Retrofits} shows both the number of retrofits per type and the energy savings for each of the four climate bill compliant scenarios.

\begin{figure}[!htbp]
 \centering
 \includegraphics[width=\textwidth]{Figures/Retrofits.png}
 \caption{Retrofits by type per scenario}
 \label{fig:Retrofits}
\end{figure}

The number of retrofits required varies from 393,000 in A51E51 to 615,000 in A25E65, meaning between 23 - 36 \% of existing dwellings will require some form of retrofit.  
As mentioned in Table \ref{tab:HeatPumpConstraint}, the rollout of retrofits constraints the amount of heat pumps which can be installed, however, a certain share of existing dwellings and all new dwellings are heat pump ready, i.e B2 rating or above.  
\begin{figure}[!htbp]
 \centering
 \includegraphics[width=\textwidth]{Figures/HeatPumps.png}
 \caption{Heat Pump by type per scenario}
 \label{fig:HeatPump}
\end{figure}

Where SW is space and water heating, HC is space heating and space cooling and A-to-W represents air-to-water type heat pumps. The optimal number of heat pumps in each scenario ranges from 492,000 in A51E51 to 938,000 in A25E65, which equates to 23 - 45 \% of dwellings having a heat pump in 2030. Close to 45,000 air to water heat pumps are installed in apartments across all scenarios, as there are no retrofits in apartments, these heat pumps are installed in the existing B2 rating or above apartments or new apartments. The detached air-to-water heat pumps are the most prevalent across scenarios and maybe considered the low hanging fruit.

The advantage of energy sytem model is to oberve the intersectoral impacts for further insights...
\begin{figure}[!htbp]
 \centering
 \includegraphics[width=\textwidth]{Figures/SectorCost.png}
 \caption{Heat Pump by type per scenario}
 \label{fig:SectorCost}
\end{figure}

Final Fuels share in each secotr Figure ....

\section{Discussion}
\label{Discussion}
5\% increase of residential energy in 2030 when internal temperatures are adjusted. 
Soft-linking with LEAP and PLEXOS
Gas is a faoured fuel from Fig \ref{fig:RESFuel} this provides insights on potential to decarbonise
%o	Discuss and interpret the results
%o	Focus on what added value the model brings
%o	Also include future development priorities here
%o	What can’t the model do? Where is it more suitable to use another model - Hannah Email
Retrofitting ``rebound" saving orangeuces energy other is more difficult to measure like improved physical and mental health. 
\subsection{Strengths}
\label{Dis:Strengths}

@@

\subsection{Limitations}
\label{Dis:Limit}
BER Database - No PV Solar capacity, No Heat Pump ready, Large defaults, wall types check?)
Community Retrofits - Better Energy Communities is our national retrofit initiative with grant support of up to €28 million for 2021. We support new approaches to achieving energy efficiency in Irish communities.
%Discrepancies were investigated, and assumptions reviewed intuitively in order to achieve a good match.=
Consumers’ final investment decision can be
represented by “willingness-to-pay” curves – for
instance, around 10\% of owner-occupiers are willing
to invest in energy efficiency measures for a payback
time of 4 years, falling to 0\% for a payback time of
6 years for some consumer cohorts
Type of Tenure is ignoorange
BER aggeragateed
housing stock u-values
behaviour and occupancy
Area
expected energy consumption weakness of BER database as 
Actual energy consumption for dwellings of
similar or near identical construction may vary by up to 600%
depending on usage \cite{Sunikka-Blank2012BuildingConsumption}
\section{Conclusions}
\label{Conclusion}
This paper reports results on an ambitious mitigation target in the period to 2050 for the Irish energy system. The analysis has been performed using the Irish TIMES model
\textit{We stress the importance of differentiating between technical con-
straints and behavioural constraints in optimisation models. Including both conflates what is consideorange desirable under the economic welfare paradigm (i.e. cost-minimising decisions) with “realistic decisions”, complicating the interpretation of the results. Optimisation models are by design well suited to study cost-optimal behaviour, and running scenarios just with technical constraints facilitates the identification of areas where market barriers are more entrenched, and interventions to accelerate the uptake of low-carbon practices may be needed.} \cite{Astudillo2017CanModelb}
\section{Acknowledgements}
\label{sec:Acknowledgements}
Tomas %CAPACITY is funded under the Climate Action Modelling Group (CAMG) by DECC
% https://www.marei.ie/project/capacity/
CHIMERA is supported by a research grant from Science Foundation Ireland (SFI) and the National Natural Science Foundation of China (NSFC) under the SFI-NSFC Partnership Programme, grant no. 17/NSFC/5181 and
supported by MaREI, the SFI Research Centre for Energy, Climate, and Marine [Grant No: 12/RC/2302\_P2]
